%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Tsarakhova Milena}} & Email : \href{mailto:tsarakhova.mv@phystech.edu}{Tsarakhova.MV@phystech.edu}\\
  \href{https://github.com/MilenaTss}{https://github.com/MilenaTss} & Mobile : +7-918-705-87-94 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Applied Mathematics and Computer Science}{Sept. 2019 -- Dec. 2020}
  \resumeSubHeadingListEnd

\section{Skills}
    \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{: C++ (Intermediate), Python (Pre-Intermediate), SQL (Beginner)}
    \resumeSubItem{Libraries}{: Sqlite, SQLAlchemy, Beautifulsoup, Requests, Pygame, nltk}
    \resumeSubItem{Frameworks}{: Flask}
    \resumeSubItem{Test Skills}{: Unittest in python, Google Tests with C++}
    \resumeSubItem{Developer Tools}{: Clion, Pycharm, DataGrip}
    \resumeSubItem{Knowledge}{: Algorithms and Data Structures, OOP, Algebra, Number Theory}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/MilenaTss/Python_chatbot}{Chatbot VK}}
          {\\A parser was written for the kinopoisk website. The parser searches for movie data and saves it to the database.
          \\Vk api is used to create a chat bot. The bot has buttons in the functionality that you can use to select the type of movie and request a link and description for it.
          \\Libraries: Beautifulsoup, requests, sqlite}
          
    \resumeSubItem{\href{https://github.com/MilenaTss/YandexRestApi}{Python REST API}}
        {\\Implemented a REST API delivery service. It is possible to hire couriers, create orders, distribute orders to couriers, and also find out information about the courier like salary, rating, etc.
        \\Also were written extensive tests.
        \\Framework - Flask
        \\Database - SQLAlchemy}
        
   \resumeSubItem{\href{https://github.com/MilenaTss/Python_game_clicker}{Pygame clicker}}
   {\\This project implements the
   functionality of the game clicker. You can earn clicks by clicking on the space bar.
   \\It also implements its own button class, which allows you to perform an action when you click on it.
   \\Libraries: Pygame}
   
   \resumeSubItem{\href{https://github.com/MilenaTss/Markov_Chain_Text_generator}{Markov Chain text generator}}
   {\\In this project, I use chains of length 2 and length 3, to create data for which you can create texts. Accordingly, the generator based on chains of length 3 works much better, because they take into account a lot more options.
    \\You can submit any file to the generator, on the basis of which it will create new sentences.
    \\Libraries: nltk, collections}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\href{https://github.com/MilenaTss/Diplomas}{Achivements}}
  \resumeSubHeadingListStart
    \resumeSubItem{Olimpiads}
      {MIPT School olympiad in mathematics - prizewinner, 2019}
    \resumeSubItem{All-Russian School olympiads}
      {Winner of regional stage in computer science, prizewinner of regional stage in mathematics, 2019}
  \resumeSubHeadingListEnd
  
  
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Teaching}
      {Worked as a teacher of Olympiad mathematics for grades 3-7, Feb 2021 - June 2021}
      \resumeSubItem{Tinkoff Course}{QA Engineer, 2021}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
